### 2015-01-14 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Updated scripts and report with figures

@@

@@

@@

@@

@@

>>>>

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Eastside_Array}
	\caption{Test 7 (FSW7): Eastside Array}
	\label{fig:Test_7_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Westside_Array}
	\caption{Test 7 (FSW7: Westside Array}
	\label{fig:Test_7_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Hallway_Array}
	\caption{Test 7 (FSW7): Hallway Array}
	\label{fig:Test_7_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Doorway_Array}
	\caption{Test 7 (FSW7): Doorway Array}
	\label{fig:Test_7_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Eastside_Array}
	\caption{Test 7 (FSW7): Suppression Eastside Array}
	\label{fig:Test_7_Suppression_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Westside_Array}
	\caption{Test 7 (FSW7): Suppression Westside Array}
	\label{fig:Test_7_Suppression_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Hallway_Array}
	\caption{Test 7 (FSW7): Suppression Hallway Array}
	\label{fig:Test_7_Suppression_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Doorway_Array}
	\caption{Test 7 (FSW7): Suppression Doorway Array}
	\label{fig:Test_7_Suppression_Doorway_Array}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Eastside}
	\caption{Test 7 (FSW7): Eastside Heat Flux}
	\label{fig:Test_7_Eastside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Westside}
	\caption{Test 7 (FSW7): Westside Heat Flux}
	\label{fig:Test_7_Westside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Hallway}
	\caption{Test 7 (FSW7): Hallway Heat Flux}
	\label{fig:Test_7_Hallway_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Near_Fire_Room}
	\caption{Test 7 (FSW7): Heat Flux Near Fire Room}
	\label{fig:Test_7_Heat_Flux_Near_Fire_Room}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Hallway_Velocity}
	\caption{Test 7 (FSW7): Hallway Velocity}
	\label{fig:Test_7_Hallway_Velocity}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Doorway_Velocity}
	\caption{Test 7 (FSW7): Doorway Velocity}
	\label{fig:Test_7_Doorway_Velocity}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Eastside_Array}
	\caption{Test 8 (FSE8): Eastside Array}
	\label{fig:Test_8_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Westside_Array}
	\caption{Test 8 (FSE8): Westside Array}
	\label{fig:Test_8_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Hallway_Array}
	\caption{Test 8 (FSE8): Hallway Array}
	\label{fig:Test_8_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Doorway_Array}
	\caption{Test 8 (FSE8): Doorway Array}
	\label{fig:Test_8_Doorway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Eastside_Array}
	\caption{Test 8 (FSE8): Suppression Eastside Array}
	\label{fig:Test_8_Suppression_Eastside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Westside_Array}
	\caption{Test 8 (FSE8): Suppression Westside Array}
	\label{fig:Test_8_Suppression_Westside_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Hallway_Array}
	\caption{Test 8 (FSE8): Suppression Hallway Array}
	\label{fig:Test_8_Suppression_Hallway_Array}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Doorway_Array}
	\caption{Test 8 (FSE8): Suppression Doorway Array}
	\label{fig:Test_8_Suppression_Doorway_Array}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Eastside}
	\caption{Test 8 (FSE8): Eastside Heat Flux}
	\label{fig:Test_8_Eastside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Westside}
	\caption{Test 8 (FSE8): Westside Heat Flux}
	\label{fig:Test_8_Westside_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Hallway}
	\caption{Test 8 (FSE8): Hallway Heat Flux}
	\label{fig:Test_8_Hallway_Heat_Flux}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Near_Fire_Room}
	\caption{Test 8 (FSE8): Heat Flux Near Fire Room}
	\label{fig:Test_8_Heat_Flux_Near_Fire_Room}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Hallway_Velocity}
	\caption{Test 8 (FSE8): Hallway Velocity}
	\label{fig:Test_8_Hallway_Velocity}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Doorway_Velocity}
	\caption{Test 8 (FSE8): Doorway Velocity}
	\label{fig:Test_8_Doorway_Velocity}
\end{figure}
